---
title: "Vestib_09202017"
author: "P. Hoover"
date: "September 20, 2017"
output: 
  html_document:
    include:
      in_header: test.html
    theme: flatly
    highlight: tango

---

```{r setup, include=FALSE}
#Load Libraries
library(dplyr)
library(xlsx)
library(tidyr)
library(reshape2)
library(ggplot2)
library(knitr)
library(rmarkdown)
library(DT)
library(car)

#Set Global Chunk Options
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(fig.width=8,fig.height=8,echo=TRUE,warning=FALSE,message=FALSE) 

#Load Datasets
load("final_df.RData")

means<-function(x){
  mean(x,na.rm=TRUE)
}

sds<-function(x){
  sd(x,na.rm=TRUE)
}

gender<-final_df%>%group_by(Gender)%>%summarise(N=n())%>%mutate(Percent=round(N/sum(N)*100,2))%>%arrange(desc(N))
service<-final_df%>%group_by(Service)%>%summarise(N=n())%>%mutate(Percent=round(N/sum(N)*100,2))%>%arrange(desc(N))

final_df$Age_lbl<-ifelse(final_df$Age>18&final_df$Age<25,"20 to 24",
                         ifelse(final_df$Age>24&final_df$Age<30,"25 to 29",
                                ifelse(final_df$Age>29&final_df$Age<35,"30 to 34",
                                       ifelse(final_df$Age>34&final_df$Age<40,"35 to 39",
                                              ifelse(final_df$Age>39&final_df$Age<45,"40 to 44",
                                                     ifelse(final_df$Age>44&final_df$Age<50,"45 to 49",
                                                            ifelse(final_df$Age>49&final_df$Age<55,"50 to 54",
                                                                   ifelse(final_df$Age>54,"55 to 60",NA))))))))

final_df$Age_lbl<-factor(final_df$Age_lbl,levels=c("20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "45 to 49", "50 to 54", "55 to 60" ))
age<-final_df%>%group_by(Age_lbl)%>%summarise(N=n())%>%mutate(Percent=round(N/sum(N)*100,2))

final_df$symp_tot<-rowSums(final_df[,c(41:45)]=="X")
final_df$SOT<-as.numeric(final_df$SOT)
final_df$FGA<-sub("/30","",final_df$FGA)
final_df$FGA<-as.numeric(final_df$FGA)

```

## Demographic Information


<center> Total Patients: `r length(unique(final_df$ID))` </center>

<center> Time in Service:  `r round(means(final_df$TimeInService),2)` &plusmn; `r round(sds(final_df$TimeInService),2)` </center>

<center> Average Patient Age: `r round(means(final_df$Age),2)` &plusmn; `r round(sds(final_df$Age),2)` </center>

***

<h4> Patient Age Labeled:  </h4>

***

`r kable(age)`

***

<h4> Gender Counts: </h4> 

*** 

`r kable(gender)` 

***

<h4> Service Counts: </h4> 

***

`r kable(service)` 

***
##Central Counts 

***
<center> Average Central Counts: `r round(means(final_df$Total_C),2)` &plusmn; `r round(sds(final_df$Total_C),2)` </center>

<center> Median Central Counts: `r round(median(final_df$Total_C,na.rm=TRUE),2)` </center>

<center> Total Number of Central Tests: ~17 </center>

***
&nbsp; 
```{r Vestib, include=TRUE,echo=FALSE,fig.align='center'}
ccount<-final_df%>%
  group_by(Total_C)%>%
  summarise(N=n())%>%
  mutate(Perc=round(N/sum(N)*100,2))%>%
  filter(!is.na(Total_C))

kable(ccount)

ggplot(final_df,aes(x=Total_C))+geom_bar(fill="navyblue",binwidth = .5)+ggtitle("Histogram of Total Number of Central Signs")+theme(plot.title=element_text(hjust=0.5,vjust=0.1))+scale_y_continuous(expand=c(0,0))+xlab("Total Number of Centeral Signs")+ylab("Frequency")+expand_limits(y=c(0,175))
```


#Patient Complaints

```{r complains, include=TRUE,echo=FALSE}
symp<-final_df[,grep("\\_Present",names(final_df))]
total<-rowSums(symp[]=="X")


```

<center> Average Number of Patient Symptoms: `r round(means(total),2)` &plusmn; `r round(sds(total),2)` </center>

```{r symp counts,include=TRUE,echo=FALSE}
symps<-symp%>%
  summarise_all(funs(N=sum(.=="X")))%>%
  gather()%>%
  mutate(Prop=round(value/773*100,2))
symps[,1]<-gsub("\\_Present_N","",symps[,1])
names(symps)<-paste(c("Symptoms","N","Perc"))

kable(symps)
```

#Central Signs

```{r vestib compare, include=TRUE, echo=FALSE}
abnormals<-final_df[,grep("\\_Abnormal",names(final_df))]

abs<-abnormals%>%
  summarise_all(funs(sum(.=="C",na.rm=TRUE)))%>%
  gather()%>%
  arrange(desc(value))%>%
  mutate(P=round(value/773*100,2))%>%
  filter(!value==0)
abs[,1]<-gsub("\\_Abnormal","",abs[,1])
abs[,1]<-gsub("\\Vestibular_","",abs[,1])
names(abs)<-paste(c("Test","Sum","Perc"))
kable(abs)
```


#Variable Exploration {.tabset}
##Demographics Against Total Central
```{r dem_scatter, include=TRUE, echo=FALSE,fig.width=10,fig.height=10}
#Formulas
dem<-(~Age+LOC+AOC+PTA+TimeInService+symp_tot+Total_C)
sur<-(~ABC_Tot_Score+NSI_Tot_Score+PCLM_Tot_Score+PHQ9_Tot_Score+GAD7_Tot_Score+DHI_Tot_Score+FGA+SOT+Total_C)

scatterplotMatrix(dem,data=final_df)
```

##Surveys Against Total Central
```{r survey_scatter,include=TRUE, echo=FALSE,fig.width=10,fig.height=10}
scatterplotMatrix(sur,data=final_df)
```


##Variable Significance Testing {.tabset}
#Regression Exploration
```{r reg, include=TRUE,echo=FALSE}
formula<-Total_C~ABC_Tot_Score+NSI_Tot_Score+PCLM_Tot_Score+PHQ9_Tot_Score+GAD7_Tot_Score+DHI_Tot_Score+FGA+SOT+LOC+AOC+PTA+TimeInService+symp_tot
lm_d<-final_df%>%
  select(c('ABC_Tot_Score','NSI_Tot_Score','PCLM_Tot_Score','PHQ9_Tot_Score','GAD7_Tot_Score','DHI_Tot_Score','FGA','SOT','LOC','AOC','PTA','TimeInService','symp_tot','Total_C'))
lm_d[]<-scale(lm_d)

lm(formula,data=lm_d)


```



